Community Data Science meets Digital Heritage: Controversies about World Heritage Sites in the Online Community of Wikipedia

### 2019-05-11 code/paper.Rmd
diff in years between start of article and inscription year

## Basic qualities of the WP articles about WH sites

@@

## Basic qualities of consumption of articles

@@

## Basic qualities of the editing process

@@

@@

What are the keywords for controversy in edit messages? And how common are these warrning messages?

@@

>>>>

## Basic qualities of the content of WP articles about WH sites

@@

## Basic qualities of the consumption of WP articles about WH sites

@@

## Basic qualities of the editing process of WP articles about WH sites

@@

bind_rows(
page_data_for_all_pages_rh_tbl %>% 
  mutate(revert = ifelse(revert, 1, 0)) %>%
  group_by(Site) %>% 
  summarise( n_revert_edits = sum(revert),
             n_edits = n()) %>% 
  mutate(prop_revert_edits = n_revert_edits / n_edits,
           Site = "World Heritage Sites"),

ten_k_random_wp_pages_revision_history_page_details %>% 
  mutate(revert = ifelse(revert, 1, 0)) %>%
  group_by(Site) %>% 
  summarise( n_revert_edits = sum(revert),
             n_edits = n()) %>% 
  mutate(prop_revert_edits = n_revert_edits / n_edits, 
         Site = "Random pages")
) %>%

   ggplot(aes(prop_revert_edits,
             fill = Site)) +
  geom_density(alpha = 0.3) +
  scale_x_log10() +
  scale_fill_viridis_d(labels = c("Random", 
                               "World Heritage")) +
  labs(x = "Proportion of reverting edits per article",
       fill = "Wikipedia pages") +
  theme_minimal()

wh_pages_talk_page_length <- 
left_join(page_data_for_all_pages,
          revision_history_page_details_wordcount)

ggplot(wh_pages_talk_page_length,
         aes(rh_n_edits,
             rh_revert_prop,
             label = str_wrap(Site, 30))) +
  geom_point(alpha = 0.5,
             aes(size =   (talk_page_wordcount),
                 colour = (talk_page_wordcount))) +
    geom_text_repel(
    data            = wh_pages_talk_page_length %>%  
                      filter(talk_page_wordcount > 8000),
    segment.size  = 0.2,
    colour = "black",
    force = 50,
    segment.color = "grey50",
    direction     = "both"
  ) +
  scale_y_log10() +
  scale_x_log10(labels = scales::comma_format(accuracy = 1)) +
  coord_fixed(1) +
  scale_color_viridis_c(name = "Talk page word count", 
                        labels = c(5000, 10000, 15000, 20000),
                        breaks = c(5000, 10000, 15000, 20000)) +
  scale_size_continuous(name = "Talk page word count", 
                        labels = c(5000, 10000, 15000, 20000),
                        breaks = c(5000, 10000, 15000, 20000)) +
   guides(color= guide_legend(), size=guide_legend()) +
  theme_minimal(base_size = 14) +
  labs(x = "Number of edits",
       y = "Proportion of edits that are reverts") +
    ggtitle("")

ggsave("figures/wh_wikpedia_pages_talk_page_wordcount_reverts_scatterplot.png")

Talk page topic modelling

@@

What are the keywords for controversy in edit messages? And how common are these warring messages?

@@

## Temporal patterns

Page ages: are WH pages younger than the typical WP page? What's their relationship to their inscription year?

```{r}
# get first and last edit, and inscription year
library(lubridate)
page_data_for_all_pages_rh_tbl_edit_start_end_span <- 
page_data_for_all_pages_rh_tbl %>% 
  group_by(Site) %>% 
  summarise(first_edit_date = min(rh_date),
            last_edit_date = max(rh_date),
            edit_span = last_edit_date - first_edit_date) %>% 
  mutate(Site = as.numeric(Site)) %>% 
  arrange(Site) %>% 
  bind_cols(page_data_for_all_pages) %>% 
  mutate(inscription_year = as.Date(ISOdate(Year_num, 1, 1))) %>% 
  mutate(diff_first_edit_inscription_year = as.numeric(ymd_hms(first_edit_date) - as.POSIXlt(inscription_year)) / 365 )

ggplot(page_data_for_all_pages_rh_tbl_edit_start_end_span, 
       aes(diff_first_edit_inscription_year)) +
  geom_histogram() +
  theme_minimal(base_size = 12)  +
  geom_vline(xintercept = 0, colour = "red") +
  ylim(0, 60) +
  annotate("text", x = -10, y = 55, label = "Page appeared\nbefore inscription\n←", size = 10) +
  annotate("text", x = 10,  y = 55, label = "Page appeared\nafter inscription\n→", size = 10)
